The Algorand Virtual Machine

### 2021-03-04 tex/avm.tex
Add proposal.md again
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    \section{Instruction Set Summary}\label{subsec:instruction-set-summary}

@@

    Every block of the Algorand blockchain corresponds to a set of transactions. We store the commitment of this
    transaction set in every block, but we don't keep the set itself. To be able to detect replay attacks, we require
    every signature that a user creates to have a nonce. This nonce consists of the issuance round of the signature
    and a sequence number: \texttt{(issuance,\ sequence)}. When a user creates more than one signature in a round, he
    must sequence his signatures starting from 0 (i.e.~the sequence number restarts from 0 in every round). We define
    a maximum lifetime for signatures, so a signature is invalid if \texttt{currentRound\ -\ issuance\
        \textgreater{}\ maxLifeTime} or if a signature of the same user with a bigger or equal nonce is already used
    (i.e
    .~is recorded in the blockchain). A nonce is bigger than another nonce if it has an older issuance. If two nonces
    have an equal issuance, the nonce with the bigger sequence number will be considered bigger.

    To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. When the
    difference between \texttt{issuance} component of this nonce and the current round becomes bigger than the
    maximum allowed lifetime of a signature, this information can be safely deleted. \textbf{As a result, we will not
    have the problem of " unremovable empty accounts" like Ethereum.}

@@

    \section{Incentive mechanism}\label{incentive-mechanism}

@@

    \begin{itemize}
        \item \(G\) is an undirected graph.
        \item Every vertex in \(G\) corresponds to a transaction.
        \item Vertices \(u\) and \(v\) are adjacent in \(G\) if and only if u has a memory block \(B\) in its writing
        list and \(v\) has \(B\) in either its writing list or reading list.
    \end{itemize}

    If we consider a proper vertex coloring of \(G\), every color class will give us an independent set of
    transactions that can be validated concurrently. To achieve the highest parallelization, we need to color \(G\)
    with minimum number of colors. Thus, the chromatic number of the memory dependency graph shows how good a
    transaction set could be run concurrently.

@@

    The agreement protocol, at the time step \(t\), will use \(\sum_{u}Stake_{u,t}\) to determine the required number of
    votes for the confirmation of a block. At the start of the agreement protocol, \(\beta\) is initialized to \(0\).
    If after confirming a block we have:
    \[
        \sum_{u}Stake_u < \gamma \sum_{u} Balance_u
    \]
    The protocol will increase the value of \(\beta\) to make sure that the total stake of the system goes high enough.
    If after confirming a block we have \(\beta > 0\) and:
    \[
        \sum_{u}Stake_u > \lambda \sum_{u} Balance_u
    \]
    The protocol will decrease the value of \(\beta\) until it eventually reaches \(0\) again.

>>>>

    \section{Instruction Set Summary}\label{sec:instruction-set-summary}

@@

    Every block of the Algorand blockchain corresponds to a set of transactions. We store the commitment of this
    transaction set in every block, but we don't keep the set itself. To be able to detect replay attacks, we require
    every signature that a user creates to have a nonce. This nonce consists of the issuance round of the signature
    and a sequence number: \texttt{(issuance,\ sequence)}. When a user creates more than one signature in a round, he
    must sequence his signatures starting from 0 (i.e.~the sequence number restarts from 0 in every round). We define
    a maximum lifetime for signatures, so a signature is invalid if \texttt{currentRound - issuance \textgreater{}\
        maxLifeTime} or if a signature of the same user with a bigger or equal nonce is already used
    (i.e.~is recorded in the blockchain). A nonce is bigger than another nonce if it has an older issuance. If two
    nonces have an equal issuance, the nonce with the bigger sequence number will be considered bigger.

    To be able to detect invalid signatures, we keep the maximum nonce of used digital signatures per user. When the
    difference between \texttt{issuance} component of this nonce and the current round becomes bigger than the
    maximum allowed lifetime of a signature, this information can be safely deleted. \textbf{As a result, we will not
    have the problem of "un-removable empty accounts" like Ethereum.}

@@

    \section{Incentive mechanism}\label{sec:incentive-mechanism}

@@

    \begin{itemize}
        \item \(G\) is an undirected graph.
        \item Every vertex in \(G\) corresponds to a transaction.
        \item Vertices \(u\) and \(v\) are adjacent in \(G\) if and only if \(u\) has a memory block \(B\) in its
        writing list and \(v\) has \(B\) in either its writing list or reading list.
    \end{itemize}

    If we consider a proper vertex coloring of \(G\), every color class will give us an independent set of
    transactions which can be validated concurrently. To achieve the highest parallelization, we need to color \(G\)
    with minimum number of colors. Thus, the chromatic number of the memory dependency graph shows how good a
    transaction set could be run concurrently.

@@

    The agreement protocol, at the time step \(t\), will use \(\sum_{u}Stake_{u,t}\) to determine the required number of
    votes for the confirmation of a block. At the start of the agreement protocol, \(\beta\) is initialized to \(0\).
    If after confirming a block we have:
    \[
        \sum_{u}Stake_u < \gamma \sum_{u} Balance_u
    \]
    The protocol will increase the value of \(\beta\) to make sure that the total stake of the system is not too low.

    If after confirming a block we have \(\beta > 0\) and:
    \[
        \sum_{u}Stake_u > \lambda \sum_{u} Balance_u
    \]
    The protocol will decrease the value of \(\beta\) until it eventually reaches \(0\) again.
